---
title: "Introduction to binomial package"
author: "Carolus Chan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```


## Binomial Distribution

'binomial' is a package that is met to calculate and plot binomial probabilities and associated statistics. 


## bin_choose 

Given the number of trials `n` and successes `k`, one can use `bin_choose` to calculate the number of combinations

```{r}
bin_choose(n = 5, k = 2)
```


## bin_probability

Given number of trials `trials` and successes `success` and probability of success `prob`, one can use `bin_probability` to calculate the binomial probability. 

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```


## bin_distribution

Given number of trials `trials` and probability of success `prob`, one can use `bin_distribution` to generate a binomial distribution. In addition, `bin_distribution` has a plot function to visualize the distribution. 

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)
```

## bin_cumlative 

Given number of trials `trials` and probability of success `prob`, one can use `bin_cumlative ` to generate a binomial distribution with the cumulative success probablity. In addition, `bin_cumlative ` has a plot function to visualize the cumulative distribution. 

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)
```

## bin_variable

`bin_variable` takes `trials` and `prob` and generates summary statistics: mean, variance, mode, skewness, kurtosis. You can use "bin_" followed by the desired statistic to get each on individually. 

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1

bin_mean(trials = 10, p = 0.3)
```

